Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-12 manuscript/manuscript.tex
Improve D determination text

We perform comparisons between the analytical solutions for the spherical shell and the
numerical integration results for linear and exponential density functions.
From these results, we generalize default values for $D$ and $\delta$ that ensure a
numerical error lower than 0.1\% of the spherical shell values.

\begin{table}
\caption{
    Description of the tesseroid models used to build a spherical shell and characterize
    the accuracy of the numerical integration.
    The first three columns describe the shapes of the tesseroid models: each one
    specifies the number of tesseroids on the corresponding dimension (radial,
    latitudinal, longitudinal).
    The last two columns specify the latitudinal and longitudinal size of each
    tesseroid that compose the spherical shell model.
    The outer radius of the shell is equal to the mean Earth radius, while the inner
    radius is defined based on its thickness.
    For each shape, we define several spherical shell models with the following
    thicknesses: 100m, 1km, 10km, 100km and 1000km.
}
\label{tab:tess-models}
\begin{tabular}{cccccc}
    Radial & Latitudinal & Longitudinal  & Total tesseroids & $L_\phi$ & $L_\lambda$
    \\ \hline
    1 & 1  & 2  & 2   & 180$^\circ$ & 180$^\circ$ \\
    1 & 6  & 12 & 72  &  30$^\circ$ &  30$^\circ$ \\
    1 & 12 & 24 & 288 &  15$^\circ$ &  15$^\circ$ \\
    1 & 18 & 36 & 648 &  10$^\circ$ &  10$^\circ$ \\
\end{tabular}
\end{table}

@@

In order to compare the numerical results with the analytical solution we
must build spherical shell models made of tesseroids.
We propose the ones detailed on Table~\ref{tab:tess-models}: the outer radius of each
shell is equal to the mean Earth radius (6378.137 km) while the inner radius is
determined based on its thickness.
We cover spherical shells composed by tesseroid of different sizes and shells with
thicknesses of 100m, 1km, 10km, 100km and 1000km.

>>>>

We perform comparisons between the analytical solutions for the spherical shell and the
numerical integration results for linear, exponential and trigonometric density
functions.
From these results, we generalize default values for $D$ and $\delta$ that ensure a
numerical error lower than 0.1\% of the spherical shell values.

\begin{table}
\caption{
    Description of the tesseroid collections used to build a spherical shell and
    characterize the accuracy of the numerical integration.
    The first three columns describe the shapes of the tesseroid collections: each one
    specifies the number of tesseroids on the corresponding dimension (radial,
    latitudinal, longitudinal).
    The last two columns specify the latitudinal and longitudinal size of each
    tesseroid that compose the spherical shell model.
    For each collection, we define four spherical shell models with an outer radius
    equal to the mean Earth radius (6378.137 km) and the inner radius determined by the
    following thicknesses: 100m, 1km, 10km, 100km and 1000km.
}
\label{tab:tess-models}
\begin{tabular}{cccccc}
    Radial & Latitudinal & Longitudinal  & Total tesseroids & $L_\phi$ & $L_\lambda$
    \\ \hline
    1 & 1  & 2  & 2   & 180$^\circ$ & 180$^\circ$ \\
    1 & 6  & 12 & 72  &  30$^\circ$ &  30$^\circ$ \\
    1 & 12 & 24 & 288 &  15$^\circ$ &  15$^\circ$ \\
    1 & 18 & 36 & 648 &  10$^\circ$ &  10$^\circ$ \\
\end{tabular}
\end{table}

@@

In order to compare the numerical results with the analytical solution we
must build spherical shell models made of tesseroids.
These shell models are determined by their inner and outer radii and by the collection
of tesseroids used to build the shell.
For this analysis we have chosen to set the outer radii of every shell model equal to
the mean Earth radius (6378.137 km), while the inner radius is determined by the desired
thickness of the shell.
We choose  different values of shell thickness (100m, 1km, 10km, 100km and 1000km) in
order to account for different computation scenarios.
Furthermore, we propose different tesseroids collections to build the shell model by
regularly splitting it along the longitudinal and latitudinal directions.
Each collection, described in Table~\ref{tab:tess-models}, is composed by a different
number of tesseroids, i.e. with tesseroids of different sizes.
Finally, for each collection we build a shell model with the thicknesses
previously described, giving a total of 20 different shell models.
